---
title: "NEURO_EXAM"
author: "LAURA PAAABY"
date: "5/5/2022"
output: html_document
---

## Behavioural Analysis of The Optimus Prime Experiment 
this is made to see whether the prime had any effect in the reaction time

```{r}
pacman::p_load(tidyverse, lme4, lmerTest, tidytext, car, devtools, maps, xtable, shiny, caret, dplyr, tidyr, stringr, kableExtra, formattable,qwraps2, sjPlot)
```

*LOADING DATA*
```{r}
data <- read_csv("behave_data_neuro.csv")
head(data)
```
#### GETTING R TIME OUT AS A LIST 
```{r}
rt <- list(data$rt)
write.csv(rt,"rt.csv",row.names = T)

mean(data$rt)

```



### models 

**MIXED EFFECT: RT ~ PRIME (1|TRIAL_NUMBER)**
lets see how well the reaction time are predicted by the prime, with trial_number as the random effect.
```{r}
m_react <- lmer(rt ~ prime + (1|trial_number), data = data, 
    control=lmerControl(check.nobs.vs.nlev = "ignore",
     check.nobs.vs.rankZ = "ignore",
     check.nobs.vs.nRE="ignore"))

summary(m_react)
```
There are no significant difference in the reaction time whether you are primed spatially, with color or not at all. 

**LINEAR MODEL: RT ~ PRIME**
```{r}
lin_rt <- lm(rt_fix ~ prime_new, data)
summary(lin_rt)
```

# NOW TIME FOR THE REAL MODELS - GLMER
this must be done since the reaction time is not normally distributed :p 
```{r}
hist(data$rt, breaks = 100)
```
i argue this looks very GAMMA like distributed, thus a glmer is used

#### for all **five prime conditions**

```{r}
model_glm <- glmer(rt ~ prime + (1|trial_number), family = Gamma, data = data)
summary(model_glm)
```


Okay here we can actually see some significant differences in the reaction time - however, here we distinquish between the red/blue prime and the left/right spatial prime, which i am not interested in. I thus combine these columns:


### for **three priming conditions**
```{r}
data$prime_new <- ifelse(data$prime == 'red'|data$prime == 'blue', 'colour', ifelse(data$prime == 'left' | data$prime == 'right', 'spatial', 'Anoprime'))

data$prime_num <- ifelse(data$prime == 'red'|data$prime == 'blue', '1', ifelse(data$prime == 'left' | data$prime == 'right', '2', '3'))

#### just checking if it matches 
try <- tibble(data$prime, data$prime_new)
try

m<-mean(data$rt)
sd<-sd(data$rt)
out.u<-m+2*sd

data$rt_fix<-ifelse(data$rt>out.u,NA,data$rt)

```

## MODEL TIME:
```{r}
model_glm_p <- glmer(rt_fix ~ prime_new + (1|trial_number), family = Gamma, data = data)
summary(model_glm_p)

p <- sum((residuals(model_glm_p))^2)
pre
```


### visualizing the difference in reaction time
```{r}
## fixed rt:
m<-mean(data$rt)
sd<-sd(data$rt)
out.u<-m+2*sd

data$rt_fix<-ifelse(data$rt>out.u,NA,data$rt)


p<-ggplot(data, aes(x=prime_new, y=rt_fix, colour=prime_new)) +
  stat_boxplot(geom = "errorbar", width = 0.2) +
  geom_boxplot() + labs(title = "Reaction Time in the Different Prime Conditions ", 
                        x = "Prime Type",
                        y = "Reaction Time") +
  scale_color_grey() + theme_classic() 

p
```






