---
title: "EEG_MODELS"
author: "LAURA PAAABY"
date: "5/5/2022"
output: html_document
---
## EEG Analysis of The Optimus Prime Experiment 

This is made on the preprocessed data, where I have made the data set in choosing the time periods and channels of interest regarding each of the components  

*libraries*
```{r}
pacman::p_load(tidyverse, lme4, lmerTest, tidytext, car, devtools, maps, xtable, shiny, caret, dplyr, tidyr, stringr, kableExtra, formattable,qwraps2, MuMIn)
```


# **P100**
*read data*
```{r, message=FALSE}
no_prime100 <- read_csv("P100_DATA/No100Prime.csv")
prime100 <- read_csv("P100_DATA/General100Prime.csv")
col_prime100 <- read_csv("P100_DATA/Col100Prime.csv")
spa_prime100 <- read_csv("P100_DATA/Spa100Prime.csv")

#Now we add a column in each of them called *prime type*

no_prime100$prime_type <- "ANoPrime"
prime100$prime_type <- "GeneralPrime"
col_prime100$prime_type <- "ColPrime"
spa_prime100$prime_type <- "SpaPrime"

###then we have to call the name of the 
###lets now make it all one big data set:

data_100 <- Reduce(function(...) merge(..., all=TRUE), list(col_prime100, spa_prime100, no_prime100))

### changing the names, so it isn't called levels:
data_100 <- data_100 %>% 
  rename(Trials = level_0) %>% 
  rename(Channels = level_1) %>% 
  rename(SignalInTimeWindow = level_2)

#hist(data_100$signal, breaks = 100)

```
the signals looks normally distributed, thus we continue with a 

### MODEL TIME 
First ill make a 
```{r}
model100 <- lmer(signal ~ prime_type + (1|Trials), data = data_100, 
    control=lmerControl(check.nobs.vs.nlev = "ignore",
     check.nobs.vs.rankZ = "ignore",
     check.nobs.vs.nRE="ignore"))

summary(model100)
r.squaredGLMM(model100)
#qqnorm(resid(model100))
```
okay somehow we manage to get significant results here .... 
```{r}
model100 <- lm(signal ~ prime_type, data = data_100)
summary(model100)
```




# **P200**
*read data*
```{r, message=FALSE}
no_prime200 <- read_csv("P200_DATA/No200Prime.csv")
prime200 <- read_csv("P200_DATA/General200Prime.csv")
col_prime200 <- read_csv("P200_DATA/Col200Prime.csv")
spa_prime200 <- read_csv("P200_DATA/Spa200Prime.csv")


#Now we add a column in each of them called *prime type*
no_prime200$prime_type <- "ANoPrime"
prime200$prime_type <- "GeneralPrime"
col_prime200$prime_type <- "ColPrime"
spa_prime200$prime_type <- "SpaPrime"

#then we have to call the name of the 
#lets now make it all one big data set:

data_200 <- Reduce(function(...) merge(..., all=TRUE), list(col_prime200, spa_prime200, no_prime200))

### changing the names, so it isn't called levels:
data_200 <- data_200 %>% 
  rename(Trials = level_0) %>% 
  rename(Channels = level_1) %>% 
  rename(SignalInTimeWindow = level_2)

#hist(data_200$signal, breaks = 100)

```
the signals looks normally distributed, thus we continue with a 

### MODEL TIME 
First ill make a 
```{r}
model200 <- lmer(signal ~ prime_type + (1|Trials), data = data_200, 
    control=lmerControl(check.nobs.vs.nlev = "ignore",
     check.nobs.vs.rankZ = "ignore",
     check.nobs.vs.nRE="ignore"))

summary(model200)
r.squaredGLMM(model200)
#qqnorm(resid(model200))
```



# **N170**
*read data*
```{r, message=FALSE}
no_prime170 <- read_csv("N170_DATA/No170Prime.csv")
prime170 <- read_csv("N170_DATA/General170Prime.csv")
col_prime170 <- read_csv("N170_DATA/Col170Prime.csv")
spa_prime170 <- read_csv("N170_DATA/Spa170Prime.csv")


#Now we add a column in each of them called *prime type*
no_prime170$prime_type <- "ANoPrime"
prime170$prime_type <- "GeneralPrime"
col_prime170$prime_type <- "ColPrime"
spa_prime170$prime_type <- "SpaPrime"

#then we have to call the name of the 
#lets now make it all one big data set:

data_170 <- Reduce(function(...) merge(..., all=TRUE), list(col_prime170, spa_prime170, no_prime170))

### changing the names, so it isn't called levels:
data_170 <- data_170 %>% 
  rename(Trials = level_0) %>% 
  rename(Channels = level_1) %>% 
  rename(SignalInTimeWindow = level_2)

#hist(data_170$signal, breaks = 100)
```

### MODEL TIME - N170
```{r}
model170 <- lmer(signal ~ prime_type + (1|Trials), data = data_170, 
    control=lmerControl(check.nobs.vs.nlev = "ignore",
     check.nobs.vs.rankZ = "ignore",
     check.nobs.vs.nRE="ignore"))

summary(model170)
r.squaredGLMM(model170)
#qqnorm(resid(model170))
```



# **N400**
*read data*
```{r, message=FALSE}
no_prime400 <- read_csv("N400_DATA/No400Prime.csv")
prime400 <- read_csv("N400_DATA/General400Prime.csv")
col_prime400 <- read_csv("N400_DATA/Col400Prime.csv")
spa_prime400 <- read_csv("N400_DATA/Spa400Prime.csv")


#Now we add a column in each of them called *prime type*
no_prime400$prime_type <- "ANoPrime"
prime400$prime_type <- "GeneralPrime"
col_prime400$prime_type <- "ColPrime"
spa_prime400$prime_type <- "SpaPrime"

#then we have to call the name of the 
#lets now make it all one big data set:

data_400 <- Reduce(function(...) merge(..., all=TRUE), list(col_prime400, spa_prime400, no_prime400))

### changing the names, so it isn't called levels:
data_400 <- data_400 %>% 
  rename(Trials = level_0) %>% 
  rename(Channels = level_1) %>% 
  rename(SignalInTimeWindow = level_2)

#hist(data_400$signal, breaks = 100)
var(data_400$signal)
```


### MODEL TIME - N400
```{r}
model400 <- lmer(signal ~ prime_type + (1|Trials), data = data_400, 
    control=lmerControl(check.nobs.vs.nlev = "ignore",
     check.nobs.vs.rankZ = "ignore",
     check.nobs.vs.nRE="ignore"))

summary(model400)
r.squaredGLMM(model400)
#qqnorm(resid(model400))

```

### consider looking at the lads 


#### LOOKING AT CHANNELS ...
```{r}
model_channels <- lmer(signal ~ prime_type + (1|Channels), data = data_400, 
    control=lmerControl(check.nobs.vs.nlev = "ignore",
     check.nobs.vs.rankZ = "ignore",
     check.nobs.vs.nRE="ignore"))

summary(model_channels)
```





```{r}
library(sjPlot)
library(sjmisc)

sjp.lmer(model_channels, vars = "signal", type = "ri.slope")



```












### LEVENES TEST 
```{r}
y <- c(data_100$signal, data_200$signal, data_170$signal, data_400$signal)
group <- as.factor(c(rep(1, length(data_100$signal)), rep(2, length(data_170$signal)), rep(3, length(data_200$signal)), rep(4, length(data_400$signal))))

leveneTest(y, group)
```

